A general and efficient representation of Ancestral Recombination Graphs

### 2022-04-07 paper.tex
Update Fig 1 caption to refer to A, B, C

\end{tikzpicture}
\caption{\label{fig-arg-data-structure}
Node vs edge breakpoint annotations.
The classical approach described by Griffiths
equates graph nodes with events in the stochastic process,
and associates recombination breakpoint information with \emph{nodes} (left).
This encoding
is limited in the patterns of inheritance that can be described
and requires that edges be ordered to avoid ambiguity.
The alternative is to associate breakpoint annotations
with \emph{edges} (right).
Associating the interval of genome inherited by the child node
from the parent with the corresponding edge allows
any pattern genetic inheritance to be described and does
not require edges to be ordered.
}
\end{figure}

>>>>

\end{tikzpicture}
\caption{\label{fig-arg-data-structure}
A classical ARG (subfigure B), contrasting node with edge breakpoint annotations.
(A) recombination breakpoint information encoded on \emph{nodes}.
This encoding is limited in the patterns of inheritance that can be
described and requires that edges be ordered to avoid ambiguity.
(C) breakpoint annotations associated with \emph{edges}.
Associating the interval of genome inherited by the child node
from the parent with the corresponding edge allows
any pattern genetic inheritance to be described and does
not require edges to be ordered.
}
\end{figure}
